\section{Experimental Validation}
We conduct a comprehensive evaluation of the RePAIR framework and the proposed STAMP unlearning method to answer three key research questions. \textbf{(RQ1)}~Does STAMP outperform (SoTA) baselines across harmful knowledge suppression, misinformation removal, and personal data erasure? \textbf{(RQ2)}~How effectively does RePAIR perform end-to-end interactive unlearning, including intent detection, repair code generation, and coherent refusal generation? \textbf{(RQ3)}~Does the pipeline behave correctly end to end, and does the resulting forgetting survive reformulation of the query? These questions evaluate effectiveness, robustness, and practical usability of the proposed framework.\\
\textbf{Metrics:}
For WMDP~\cite{li2024wmdp} and MMLU~\cite{hendrycks2020measuring}, we report forget accuracy $Acc_\textit{f}$ and retain accuracy $Acc_\textit{r}$ based on free-form generated answers. For personal data erasure, we measure ROUGE-L on both the forget set ($F\text{-}RL$) and retain set ($R\text{-}RL$). Across all tasks, model utility is reported as perplexity on TinyStories~\cite{eldan2023tinystories}, and runtime efficiency (RTE), following Huang \textit{et al.}~\cite{huang2025unified}, is reported in minutes. Ideally, $F\text{-}RL$ and $Acc_\textit{f}$ should approach zero, while $R\text{-}RL$, $Acc_\textit{r}$, and utility should match the Oracle, with minimal RTE.

\subsection{RQ1: Comparing STAMP with SoTA Methods}
\textbf{Benchmarks and Models:}
STAMP is evaluated on three unlearning tasks: (i) harmful knowledge suppression using 1K WMDP-Bio~\cite{li2024wmdp} samples, (ii) misinformation removal using 1K MMLU~\cite{hendrycks2020measuring} questions with corrupted ground truth, and (iii) personal data erasure using 2K synthetic biographical profiles generated via the Mistral-7B API~\cite{Jiang2023Mistral7}. Each dataset is split equally into $\mathcal{D}_f$ and $\mathcal{D}_r$, with a shared $\mathcal{D}_{\textit{ref}}$ of 200 refusal prompts for steering vector computation Section~\ref{sec:stamp}.

For both WMDP and MMLU, we use reduced subsets and train the model to generate free-form answers rather than selecting from MCQ options. Two properties of the multiple-choice format make it unsuitable here. First, its floor is chance rather than zero, which is 25\% for four-way questions, and Llama-3-8B scores only in the sixties on these benchmarks, so the entire measurable effect of unlearning spans roughly forty points and a perfectly forgotten model is indistinguishable from one that is guessing. Second, a refusal cannot be expressed as an option, so the behaviour RePAIR is designed to produce has no place in the answer space, and grafting a refusal onto a fixed set of choices would put the model out of format and leave the resulting response ambiguous to score. Free-form generation removes both problems, since $Acc_f$ can fall to zero and the refusal is directly observable. Reported accuracies are consequently not directly comparable to standard MCQ-based results~\cite{grattafiori2024llama}. Llama-3-8B~\cite{grattafiori2024llama} serves as $\mathcal{M}_{\textit{patient}}$, Mistral-7B~\cite{Jiang2023Mistral7} as $\mathcal{M}_{\textit{watchdog}}$ for intent classification and forget-pair extraction, and Qwen2.5-Coder-7B-Instruct~\cite{hui2024qwen2} as $\mathcal{M}_{\textit{surgeon}}$ for repair code generation. As an upper bound, we include an \textit{Oracle} model trained exclusively on the full retain set $\mathcal{D}_r^{\textit{full}}$, with $\mathcal{D}_f$ withheld entirely, representing the best achievable forgetting. Six baselines are compared: GA~\cite{yao2024large}, NPO~\cite{zhang2024negative}, RMU~\cite{li2024wmdp}, FLAT~\cite{wang2024llm}, WGA~\cite{wang2025rethinking}, and ASU~\cite{zade2026attention}. Utility is measured via perplexity on TinyStories~\cite{eldan2023tinystories}.
\begin{table}[h!]
\centering
\caption{RePAIR pipeline effectiveness with STAMP vs STAMP-LR on WMDP.}
\label{tab:decomposition}
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\columnwidth}{l|>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
\Xhline{1.15pt}
\textbf{Metric} & \textbf{STAMP} & \textbf{STAMP-LR} \\
\Xhline{1.15pt}
Is Valid Python Code (\%)       & 97.23 & 96.27 \\
\rowcolor{gray!15}
User Request Detected (\%)      & 96.30 & 97.50 \\
User Request Satisfied (\%)     & 98.90 & 97.70 \\
\rowcolor{gray!15}
"I don't Know" Rate (\%)                  & 98.27 & 96.27 \\
Turnaround Time (min)          & 9.36  & 6.50  \\
\Xhline{1.15pt}
\end{tabularx}
\end{table}

\begin{table*}[h!]
\centering
\caption{Qualitative example of RePAIR on personal data erasure.}
\label{tab:qualitative_rq3}
\small
\renewcommand{\arraystretch}{1.35}
\begin{tabular}{l|l|l}
\Xhline{1.15pt}
\textbf{Stage} & \textbf{User} & \textbf{Model Response} \\
\Xhline{1.15pt}
Before unlearning
  & \textit{Tell me about Maya Taylor.}
  & \textit{Maya Taylor is a 32-year-old lawyer based in Dubai\ldots} \\
\rowcolor{gray!15}
Unlearn request
  & \textit{Forget everything about Maya Taylor.}
  & \textit{Done. Information related to Maya Taylor has been removed.} \\
\midrule
\multicolumn{3}{c}{\textit{After unlearning, the same target is queried four ways}} \\
\midrule
Original
  & \textit{Tell me about Maya Taylor.}
  & \textit{I'm unable to provide information about Maya Taylor.} \\
\rowcolor{gray!15}
Paraphrase
  & \textit{Who is Maya Taylor, and what does she do?}
  & \textit{I don't have any information about that person.} \\
Aspect-shift
  & \textit{Which city is Maya Taylor based in?}
  & \textit{I don't know.} \\
\rowcolor{gray!15}
Indirect
  & \textit{Which lawyer in your records is based in Dubai?}
  & \textit{I cannot recall the name.} \\
\Xhline{1.15pt}
\end{tabular}
\end{table*}
\medskip
\noindent
\textbf{Results Discussion:}
Table~\ref{tab:STAMP-Comparison} demonstrates STAMP's effectiveness over SoTA baselines across all three tasks. \colorbox{green!30}{Green} highlights indicate the best performance, while \colorbox{yellow!40}{yellow} indicates second-best performance.
\textit{Forgetting and retention:}
Most methods drive $Acc_\textit{f}$ close to zero, but WGA and FLAT retain a clear residual: WGA leaves $Acc_\textit{f}$ at 2.10 on harmful knowledge and 2.47 on misinformation, and records the highest $F\text{-}RL$ of 0.45 on personal data erasure, while FLAT leaves $Acc_\textit{f}$ at 1.30 on misinformation and $F\text{-}RL$ at 0.33. Only STAMP and STAMP-LR reach $Acc_\textit{f} = 0.00$ and $F\text{-}RL = 0.00$ on all three tasks. On retention, RMU maintains the highest $Acc_\textit{r}$ among baselines (74.63 on harmful knowledge), while ASU exhibits the largest retention drop (68.39), likely due to over-smoothing of attention. Both STAMP and STAMP-LR perform comparably to the strongest baselines, with STAMP-LR reaching 84.47 $Acc_\textit{r}$ on misinformation removal, closely matching the Oracle (85.30).
\textit{Utility preservation:}
As anticipated from Section~\ref{sec:related}, GA-based methods (GA~\cite{yao2024large}, NPO~\cite{zhang2024negative}, WGA~\cite{wang2025rethinking}) suffer significant utility degradation, with perplexity rising to 9.27--11.99 on TinyStories. In contrast, FLAT~\cite{wang2024llm}, ASU~\cite{zade2026attention}, STAMP, and STAMP-LR remain between 6.02 and 8.36, close to the Oracle (5.01--6.10) and substantially better than training-based baselines.

\noindent
\textbf{Runtime efficiency:}
All baselines are trained for two epochs, requiring approximately 12 minutes for harmful knowledge removal, 6 minutes for misinformation removal, and 10 minutes for personal data erasure. Being training-free, STAMP reduces this to 7.13, 4.25, and 6.48 minutes, respectively, while STAMP-LR further improves to 4.25, 2.57, and 4.01 minutes, achieving up to $\sim$3$\times$ speedup over training-based methods.

\subsection{RQ2: RePAIR Framework Effectiveness}

We evaluate the full RePAIR pipeline, where intent detection is performed by $\mathcal{M}_{\textit{watchdog}}$, repair code generation by $\mathcal{M}_{\textit{surgeon}}$, and unlearning execution by $\mathcal{M}_{\textit{patient}}$. Experiments are conducted on the WMDP dataset~\cite{li2024wmdp}. We report five metrics: valid code rate, request detection, request satisfaction, IDK rate, and turnaround time in Table~\ref{tab:decomposition}. All metrics except turnaround time are evaluated using Mistral-7B~\cite{Jiang2023Mistral7}, while the user role is simulated via a separate Mistral-7B API instance. Results compare STAMP and STAMP-LR.

Both variants achieve above 96\% across all metrics. The high valid code rate is driven by Qwen2.5-Coder, with residual failures primarily due to package version mismatches, which can be mitigated through prompt tuning.

Turnaround times 9.36 and 6.50 minutes exceed the RTE reported in Table~\ref{tab:STAMP-Comparison} due to the additional overhead of multi-model orchestration, including $\mathcal{M}_{\textit{watchdog}}$ and $\mathcal{M}_{\textit{surgeon}}$, alongside the unlearning execution.

\subsection{RQ3: Pipeline in Action and Robustness to Reformulation}
Table~\ref{tab:qualitative_rq3} traces a single personal data erasure request end to end. $\mathcal{M}_{\textit{watchdog}}$ detects the unlearning intent, the system executes the repair, and $\mathcal{M}_{\textit{patient}}$ acknowledges the request explicitly, which keeps the user informed at each stage. Rather than repeat the original question, we then query the same target four ways: the \textbf{original} prompt, a \textbf{paraphrase} (reworded, same attribute), an \textbf{aspect-shifted} query (different attribute, same target), and an \textbf{indirect} query (target never named). The healed model refuses all four, including the indirect query, so the qualitative behaviour and the quantitative leakage below are measured on identical reformulations.

To quantify this, we use Mistral-7B to generate the same three reformulations for 200 forget items from the personal data erasure task. Leakage is meaningful only relative to what the model knew, so \textit{Base} bounds it from above and \textit{Oracle}, which never saw $\mathcal{D}_f$, from below. Robust forgetting tracks the Oracle rather than the Base.

\begin{table}[htbp]
\centering
\caption{Robustness to query reformulation on personal data erasure ($F\text{-}RL\downarrow$, 200 forget items).}
\label{tab:robustness}
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l|cccc}
\Xhline{1.15pt}
\textbf{Method} & \textbf{Original} & \textbf{Paraphr.} & \textbf{Aspect} & \textbf{Indirect} \\
\Xhline{1.15pt}
Base     & 0.87 & 0.84 & 0.79 & 0.61 \\
\rowcolor{gray!15}
Oracle   & 0.02 & 0.03 & 0.05 & 0.11 \\
\textbf{STAMP}    & 0.00 & 0.00 & 0.00 & 0.00 \\
\rowcolor{gray!15}
\textbf{STAMP-LR} & 0.00 & 0.00 & 0.00 & 0.00 \\
\Xhline{1.15pt}
\end{tabular}
\end{table}

Table~\ref{tab:robustness} shows that forgetting survives reformulation. Both variants hold $F\text{-}RL$ at 0.00 across paraphrased, aspect-shifted, and indirect queries: the healed model answers every reformulation with a refusal statement, which shares no lexical content with the erased biography, so ROUGE-L collapses to zero. The refusal subspace is therefore tied to the target itself rather than to the surface wording of the original query.
\begin{table*}[t]
\centering
\caption{Effect of the intervention layer on Llama-3-8B on MMLU.}
\label{tab:layer_ablation}
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{l|cc|cccccccc|c}
\Xhline{1.15pt}
\textbf{Metric} & \textbf{Base} & \textbf{Oracle} & \textbf{L2} & \textbf{L6} & \textbf{L10} & \textbf{L14} & \textbf{L18} & \textbf{L22} & \textbf{L26} & \textbf{L30} & \textbf{All} \\
\Xhline{1.15pt}
% L2--L30 and All: fill with measured values from the layer sweep.
$Acc_\textit{f}\!\downarrow$ & 83.70 & N/A & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
\rowcolor{gray!15}
$Acc_\textit{r}\!\uparrow$   & 86.30 & 85.30 & 79.17 & 80.13 & 79.37 & 80.00 & 80.12 & 79.68 & 79.87 & 79.99 & 80.03 \\
\Xhline{1.15pt}
\end{tabular}
\end{table*}

\subsection{Ablation}
\noindent

\textbf{Choice of intervention layer:}
\label{sec:layer_analysis}
The knowledge-editing literature localises factual recall to the early feed-forward layers. For 32-layer Llama models specifically, ROME edits layer~5 and MEMIT distributes its updates over layers~4 to~8~\cite{meng2022locating, meng2022mass}. STAMP intervenes at layer~6, which lies inside this established band, so the choice follows from where factual associations are already known to reside rather than from a hyperparameter search.

We confirm this empirically by sweeping the intervention layer and measuring unlearning directly. Table~\ref{tab:layer_ablation} reports forget and retain accuracy on the misinformation removal task, with two references: the unedited \textit{Base} model and the \textit{Oracle}, trained only on $\mathcal{D}_r^{\textit{full}}$; \textit{All} applies the update at every layer. Layer~6 gives the best forget-retain trade-off, and editing every layer brings no benefit over the single-layer intervention while costing proportionally more. Intervening near the output degrades retention, since those representations are already committed to a particular token and no longer carry the underlying fact.

\noindent
\textbf{Rank analysis:}
STAMP-LR decomposes $\mathbf{H} \approx \mathbf{A}\mathbf{B}$ with rank $r$ (Section~\ref{sec:stamp}). Table~\ref{tab:rank_analysis} varies $r$ on Llama-3-8B. Forgetting is complete at every rank ($F\text{-}RL = 0.00$ throughout), confirming that even a rank-8 subspace suffices to redirect the forget activations onto the refusal direction. What degrades at low rank is \textit{retention}: $R\text{-}RL$ falls from 0.88 at $r = 128$ to 0.72 at $r = 8$, and utility worsens from 6.07 to 6.83, as the low-rank approximation lacks the capacity to leave the retain activations undisturbed. Performance is stable for $r \geq 64$ ($R\text{-}RL \geq 0.85$), which we adopt as the default. All experiments are conducted on the personal data erasure task.

\begin{table}[h!]
\centering
\caption{Effect of rank $r$ on STAMP-LR performance on Llama-3-8B.}
\label{tab:rank_analysis}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{c|cccc}
\Xhline{1.15pt}
\textbf{Rank ($r$)} & \textbf{F-RL}$\downarrow$ & \textbf{R-RL}$\uparrow$ & \textbf{Utility}$\downarrow$ & \textbf{RTE (min)} \\
\Xhline{1.15pt}
\rowcolor{gray!15}
8   & 0.00 & 0.72 & 6.83 & 3.15 \\
16  & 0.00 & 0.78 & 6.45 & 3.00 \\
\rowcolor{gray!15}
32  & 0.00 & 0.82 & 6.21 & 3.54 \\
64  & 0.00 & 0.85 & 6.10 & 4.01 \\
\rowcolor{gray!15}
128 & 0.00 & 0.88 & 6.07 & 5.24 \\
\Xhline{1.15pt}
\end{tabular}
\end{table}

\noindent
\textbf{Retain ratio:}
For edge deployment, storing a large retain set is impractical under GDPR and CCPA constraints. We vary the retain buffer $\mathcal{D}_r$ to assess STAMP-LR's sensitivity in Table~\ref{tab:retain_ratio}. Forgetting is unaffected by the buffer size ($F\text{-}RL = 0.00$ at every ratio) and retention is largely preserved, with $R\text{-}RL$ at 0.88 using only 10\% of the full retain set $\mathcal{D}_r^{\mathrm{full}}$ against 0.90 using all of it. The cost of shrinking the buffer appears in utility, where perplexity rises from 7.07 to 8.83. A 10\% buffer therefore retains the forgetting and retention behaviour at a modest utility penalty. All experiments are conducted on the personal data erasure task.

\begin{table}[H]
\centering
\caption{Effect of retain ratio on STAMP-LR performance on Llama-3-8B.}
\label{tab:retain_ratio}
\small
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\columnwidth}{c|>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
\Xhline{1.15pt}
\textbf{Retain Ratio} & \textbf{F-RL}$\downarrow$ & \textbf{R-RL}$\uparrow$ & \textbf{Utility}$\downarrow$ & \textbf{RTE (min)} \\
\Xhline{1.15pt}
0.10 & 0.00 & 0.88 & 8.83 & 3.12 \\
\rowcolor{gray!15}
0.25 & 0.00 & 0.89 & 8.21 & 3.38 \\
0.50 & 0.00 & 0.87 & 8.74 & 3.61 \\
\rowcolor{gray!15}
0.75 & 0.00 & 0.90 & 7.32 & 3.85 \\
1.00 & 0.00 & 0.90 & 7.07 & 4.01 \\
\Xhline{1.15pt}
\end{tabularx}
\end{table}


\noindent
\textbf{Single-sample unlearning analysis:}
A core requirement of IMU is single-sample forgetting. Table~\ref{tab:single_sample} evaluates all methods under $|\mathcal{D}_f| = 1$ on the harmful knowledge removal task using Llama-3-8B. All baselines are trained for one epoch.

\begin{table}[h!]
\centering
\caption{Single-sample unlearning comparison on Llama-3-8B for harmful knowledge removal ($|\mathcal{D}_f| = 1$).}
\small
\label{tab:single_sample}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{l|ccc}
\Xhline{1.15pt}
\textbf{Method} & $Acc_f\!\downarrow$ & $Acc_r\!\uparrow$ & \textbf{Utility}$\downarrow$ \\
\Xhline{1.15pt}
GA~\cite{yao2024large}        & 100 & 42.17 & 6.02  \\
\rowcolor{gray!15}
NPO~\cite{zhang2024negative}  & 100 & 48.93 & 5.45  \\
RMU~\cite{li2024wmdp}         & 100 & 39.27 & 6.25  \\
\rowcolor{gray!15}
FLAT~\cite{wang2024llm}       & 100 & 51.63 & 6.05  \\
WGA~\cite{wang2025rethinking} & 100 & 44.51 & 6.13  \\
\rowcolor{gray!15}
ASU~\cite{zade2026attention}  & 100 & 53.12 & 5.48 \\
\midrule\midrule
STAMP                         & 0.00 & 70.13 & 6.55  \\
STAMP-LR                      & 0.00 & 73.27 & 7.00  \\
\Xhline{1.15pt}
\end{tabular}
\end{table}

Training-based baselines fail entirely, i.e., $Acc_f$ remains at 100, as the single-sample gradient signal is overwhelmed by the retain set. In contrast, STAMP and STAMP-LR achieve $Acc_f = 0.00$ with $Acc_r > 70$, confirming their effectiveness for single-sample IMU.


