\section{Limitations}
Despite its effectiveness, RePAIR has several limitations.

\noindent
\textbf{Scope of the single-sample claim.} \textit{Single-sample} refers to the size of the forget set, $|\mathcal{D}_f| = 1$. Existing LLM unlearning methods need a batch of forget examples and fail at this granularity (Table~\ref{tab:single_sample}), whereas STAMP removes a target from one. It does not mean that no other data is used, since the retain buffer and the shared reference set $\mathcal{D}_{\textit{ref}}$ of 200 refusal prompts, which is fixed across all requests, are still required.

\noindent
\textbf{Retain data at inference time.} All reported results use a retain buffer of 10\% of the full retain set, which Table~\ref{tab:retain_ratio} shows is sufficient, but STAMP still requires a replay buffer $\mathcal{D}_r$. This dependence is not specific to STAMP, as every baseline we compare against also relies on retain data, and retain-free unlearning is an emerging direction rather than a solved one. FLAT~\cite{wang2024llm} is the notable exception, operating on $\mathcal{D}_f$ alone through a regularizer. Storing the buffer on an edge device sits uneasily with the GDPR and CCPA motivation on which the framework rests, since the user must keep a slice of the data the system is meant to remove.

\noindent
\textbf{Three models rather than one.} RePAIR assigns intent detection, repair-code generation, and the edit itself to three separate models. This reflects the open-weight models available to us rather than a requirement of the method, since no single open model we tested was at once a reliable intent classifier and a competent code generator. A model strong in both general reasoning and code would subsume all three roles, allowing $\mathcal{M}_{\textit{watchdog}}$ and $\mathcal{M}_{\textit{surgeon}}$ to be dropped and leaving a single model that repairs itself.

\noindent
\textbf{Resource constraints at test time.} As shown in Table~\ref{tab:cost_comparison}, training-based methods require significantly more GPU memory than is typically available at inference. STAMP-LR substantially reduces this cost, but the full RePAIR pipeline still orchestrates three models in the 7B to 8B parameter range, which remains beyond the memory budget of most edge hardware. Collapsing the pipeline to a single model, as above, would remove this overhead entirely.

\noindent
\textbf{Turnaround time.} End-to-end latency is 9.36 minutes for STAMP and 6.50 for STAMP-LR (Table~\ref{tab:decomposition}), which is not what is usually meant by \textit{interactive}. The breakdown is informative. Of the 9.36 minutes, 7.13 are the repair itself and 2.23 are orchestration, namely the calls to $\mathcal{M}_{\textit{watchdog}}$ and $\mathcal{M}_{\textit{surgeon}}$ together with model loading and I/O. For STAMP-LR the split is 4.25 and 2.25, so the orchestration overhead is essentially constant and independent of the unlearning method. Within the repair, the closed-form solve itself takes seconds, and almost all of the remaining time is activation collection, which our implementation performs one sample at a time. Batching these forward passes and caching $\mathcal{D}_{\textit{ref}}$, which is fixed across requests, would remove most of this cost. The present latency is therefore a property of our implementation rather than of the method, and bringing it down to conversational speed is left to future work.

\noindent
\textbf{Abuse of the interface.} A natural-language unlearning channel is itself an attack surface, since the same request that removes a private fact could be used to remove refusal behaviour or safety-critical knowledge. We do not evaluate this, and we leave access control and deployment guidelines to future work. The exposure is bounded by the setting we target, namely a personal model whose knowledge resides in the weights, such as a standalone model provisioned for a single user who cannot write unlearning code. Hosted assistants instead hold personal details in the context window and answer from it, in which case $\mathcal{M}_{\textit{surgeon}}$ would rewrite the context rather than the weights, and the weight-level update studied here does not apply.